---
title: "Ch 14 HW"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
```

##14.2 Exercises

###Exercise 1: 
"What's the difference between paste() and paste0()? What stringr function are they related to? How do they handle NA?"  
```{r}
?paste
?paste0
```

###Exercise 2:
"Describe the difference between the 'sep' and 'collapse' arguments to str_c()"
```{r}
?str_c()
```

###Exercise 3:
"Use str_length() and str_sub() to extract middle character from string. What do you do if even number if letters?"
```{r}
v1<-"Cassandra"
str_length(v1)
str_sub(v1, 5, 5)

v2<-"Carrie"
str_length(v2)
str_sub(v2, 3, 4)
```

###Exercise 4:
"What does 'str_wrap()' do? When might you want to use it?"
```{r}
?str_wrap()
```

###Exercise 5:
"What does 'str_trim()' do? What's the opposite of str_trim()?"
```{r}
?str_trim()
```

###Exercise 6:
"Write a function that turns a vector c("a","b","c") into the string 'a, b, and c'"
```{r}
v<-c("a","b","c")

v%>%
  str_c(collapse=", ")
```

##14.3.1 Exercises

###Exercise 1:
"Explain why each of these strings don’t match a \: '\', '\\', '\\\'"  

```
Okay, this section was somewhat confusing BUT from what I can gather: "\" is seen as an escape symbol, "\\" gives you a blank space, and "\\\" I don't even know
```

###Exercise 2:
"How would you match the sequence "'\ ?

```{r}
str_view("\"'\\", "\"'\\\\", match=TRUE)
```
When creating string with \ character, use \\. When matching, use \\\\????

###Exercise 3: 
What patterns will \..\..\.. match?

```
\. matched the "." character whereas . on its own matched to any charcter. Thus, \..\..\.. matches to ".charcter.character.character"
```

##14.3.2 Exercises

###Exercise 1:
"How do you match literal string $^$ ?"
```{r}
v<-"$^$"

str_view(v, "\\$\\^\\$")
```

###Exercise 2:
"Given 'stringr::words', find all words that..."
```{r}
#Start with y
str_view(stringr::words, "^y", match=TRUE)
```

```{r}
#End with x
str_view(stringr::words, "x$", match=TRUE)
```

```{r}
#Exactly 3 letters long
str_view(stringr::words, "^...$", match=TRUE)
```

```{r}
#7 letters or more
str_view(stringr::words, ".......", match=TRUE)
```

##14.3.3 Exercises

###Exercise 1:
```{r}
#Start with vowel
str_view(stringr::words, "^[aeiou]", match=TRUE)
```

```{r}
#Only contain consonants
str_view(stringr::words, "^[^aeiou]+$", match=TRUE)
```
Note from 14.3.4 "+" is equivalent to 1 or more

```{r}
#End with ed but not eed
str_view(stringr::words, "[^e]ed$", match=TRUE)
```

```{r}
#End with ing or ise
str_view(stringr::words, "ing$|ise$", match=TRUE)
```

###Exercise 2:
"Expirically verify rule i before e exept after c"
```{r}
str_view(stringr::words, "cie", match=TRUE)
str_view(stringr::words, "cei", match=TRUE)

str_view(stringr::words, "[^c]ei", match=TRUE)
str_view(stringr::words, "[^c]ie", match=TRUE)
```
Hmm...doesn't seem to be true?

###Exercise 3:
"Is q always followed by a u?"
```{r}
str_view(stringr::words, "q[^u]", match=TRUE)
```
Yup!

###Exercise 4:
"Expression that matches British English not American English"
```{r}
#???
str_view(stringr::words, "ou", match=TRUE)
```

###Exercise 5:
"Match telephone numbers as commonly written in your country"
```{r}
#Err...okay? I'll do my best?

v1<-"916-867-9309"
str_view(v1, "\\d{3}-\\d{3}-\\d{4}", match=TRUE)
```
I admit, I read ahead...

##14.3.4 Exercises

###Exercise 1:
"Describe equivalents of ?, +, * in {m,n} form"

```
? is equiv {0,1} ... 0 or 1
+ is equiv to {1,} ... 1 or more
* is equiv to {0,} ... 0 or more
```
###Exercise 2:
"Describe what this regular expressions mean"

```
^.*$
```
Equiv to "contains any character 0 or more times" In other words, this expression matches everything.

```
"\\{.+\\}"
```
Equiv to any one character or more surrounded by curly brace

```
\d{4}-\d{2}-\d{2}, match=TRUE)
```
4 digits, hyphen, 2 digits, hyphen, 4 digits

```
"\\\\{4}"
```
I believe this will match to the string "\\{4}" (I tried recreating this string, but I couldn't figure it out! Those stupid backlashes are confusing)

###Exercise 3:
"Create regular expressions to find all words that..."
```{r}
#Start with three consonants
str_view(stringr::words, "^[^aeiou]{3}", match=TRUE)

#Have three or more vowels in a row
str_view(stringr::words, "[aeiou]{3,}", match=TRUE)

#Have two or more vowel-consonant pairs in a row 
str_view(stringr::words, "([aeiou][^aeiou]){2,}", match=TRUE)
```

##14.4.1 Exercises

###Exercise 1:
```{r}
#Start or end with x
words[str_detect(stringr::words, "^x|x$")]

#Start w/ vowel end with consonant
words[str_detect(stringr::words, "^[aeiou].*[^aeiou]$")]

#Word that contains at least one of every vowel??
words[str_detect(stringr::words, "[aeiou]")]
```

###Exercise 2:
```{r}
#Word with highest number of vowels
max(str_count(words, "[aeiou]"))

words[str_count(words, "[aeiou]")==5]
```


##14.4.2 Exercises

###Exercise 1:
"red" matched to flickered...fix this!
```{r}
?str_view_all
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
more <- sentences[str_count(sentences, colour_match) > 1]
```
Okay, so I trued the ^ and $ thing, but it did not work! After a quite google search, I obtained this???

```{r}
str_view_all(more, "\\b(red)\\b")
```

###Exercise 2:
From Harvard sentence data extract...
```{r}
#First word from each sentence
first_match

#All words ending in -ing

#All plurals
```


##14.4.3 Exercises

###Exercise 1:
Find all words that come after a number like "one"
, "two", "three", etc. Pull out both number and word.
```{r}
number<-"(one|two|three|four|five|six|seven|eight|nine|ten) ([^ ]+)"

has_num <- sentences %>%
  str_subset(number) %>%
  head(10)
has_num %>% 
  str_extract(number)
```

###Exercise 2:
Find all contractions. Seperate before and after apostrophe
```{r}
#????????? ????????????
str_view(sentences, "\'", match=TRUE)

contract<-"..\'."

has_con<- sentences %>%
  str_subset(contract)
has_con%>%
  str_extract(contract)
```

##14.4.4 Exercises

###Exercise 1:
"Replace forward slashes in string with backslashes"
```{r}
v1<-"/ yo / i / hate / this"

str_replace_all(v1, "/", "\\\\")
```
Okay! For some reason I can't back a single backslash. The notes say it should be "\\" but it never works!!!

###Exercise 2:
"Implement a simple version of str_to_lower() using replace_all()"
```{r}
v1<-"Hello There"
str_replace_all(v1, c("H"="h", "T"="t"))
```

###Exercise 3:
"Switch the first and last letter in words. Which are still words?"
```{r}
blah<-str_replace_all(words, "(^.)(.*)(.$)", "\\3\\2\\1")
intersect(words, blah)
```

##14.4.5 Exercises

###Exercise 1:
Split a string like "apples, bananas, and pears" into individual components
```{r}
v1<-"apples, bananas, and pears"
str_split(v1, boundary("word"))
```

###Exercise 2:
Why is it better to split up boundary("word") than " "?
```{r}
#Well, if you look at the previous exercise, not all words a seperated by spaces: 

str_split(v1, " ")
```

###Exercise 3:
What does splitting with an empty string ("") do? Experiment, and then read the documentation.
```{r}
blah<-"la di dah, wah wah, HA!"

str_split(blah, "")
```
Ahh, so it seems to split the string by every character in the string!

##14.5 Exericses

###Exercise 1:
How would you find all strings containing \ with regex() vs. with fixed()?
```{r}

```

###Exercise 2:
What are the five most common words in setences?
```{r}

```

##14.7 Exercises

###Exercise 1:
Find the stringi functions that:
```{r}
#Count the number of words

#Find duplicate strings

#Generate random text
```

###Exercise 3:
How do you control the language that stri_sort() uses for sorting?