---
title: "Ch 15 HW"
output: html_notebook
---
```{r}
library(tidyverse)
library(forcats)
```


##15.3 Exercises

###Exercise 1:
Explore distribution of rincome
```{r}
ggplot(gss_cat, aes(rincome)) +
  geom_bar() +
  scale_x_discrete(drop = FALSE)
```
I'm guess the x coordinate labels are really long, thus they overlap? We can fix it by changing the direction of the labels!

###Exercise 2:
Most common relig? Most common partyid?
```{r}
gss_cat %>%
  count(relig)
```
Protestant is the most common relig
```{r}
gss_cat %>%
  count(partyid)
```
Independent is the most common partyid

###Exercise 3:
What does relig and denom refer to?
```{r}
View(gss_cat)

gss_cat %>%
  filter(relig=="Protestant")%>%
  count(denom)%>%
  arrange(desc(n))
```
Relig refers type of religion, and denom refers to denomination of (if) Protestant

##15.4 Exercises

###Exercise 1:
High numbers in tvhours
```{r}
gss_cat%>%
  arrange(desc(tvhours))

ggplot(gss_cat, aes(tvhours)) +
  geom_bar() +
  scale_x_discrete(drop = FALSE)
```
I suppose the mean (which I'm guessing is around 3) would be a godd summary depending on what conclusion you want to find??

###Exercise 2:
I GIVE UP

###Exercise 3:

##15.5 Exercises

###Exercise 1:

###Exercise 2:
